### 2017-02-23 readme.Rmd
update readme

Generate some random points and a raster to represent study area.
```{r}
library(raster)
set.seed(123)
N <- 100
ks <- as.data.frame(cbind(x1=runif(N, min=-10, max=10),x2=runif(N, min=-10, max=10)))
sa <- raster(nrows=100, ncols=100, xmn=-10, xmx=10,ymn=-10,ymx=10)
sa[]<-rnorm(10000)
projection(sa) <- "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0"
plot(sa)
points(ks$x1,ks$x2,pch=16)
```

How many quasi-random background points do we need? Let start with 200.
The function will plot the underlying probability of sampling intensity, the presence points (white) and the generated quasi-random background points.
```{r}
library(qrbp)
set.seed(123)
n <- 200
bkpts <- qrbp(n,dimension = 2,known.sites=ks,include.known.sites=TRUE,
              study.area = sa,inclusion.probs = NULL,sigma=1,plot.prbs=TRUE)
points(ks$x1,ks$x2,pch=16,col='white')
```

### References 
Grafström, Anton, and Yves Tillé. "Doubly balanced spatial sampling with spreading and restitution of auxiliary totals." Environmetrics 24.2 (2013): 120-131.

>>>>

<!-- Generate some random points and a raster to represent study area. -->
<!-- ```{r} -->
<!-- library(raster) -->
<!-- set.seed(123) -->
<!-- N <- 100 -->
<!-- ks <- as.data.frame(cbind(x1=runif(N, min=-10, max=10),x2=runif(N, min=-10, max=10))) -->
<!-- sa <- raster(nrows=100, ncols=100, xmn=-10, xmx=10,ymn=-10,ymx=10) -->
<!-- sa[]<-rnorm(10000) -->
<!-- projection(sa) <- "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0" -->
<!-- plot(sa) -->
<!-- points(ks$x1,ks$x2,pch=16) -->
<!-- ``` -->

<!-- How many quasi-random background points do we need? Let start with 200. -->
<!-- The function will plot the underlying probability of sampling intensity, the presence points (white) and the generated quasi-random background points. -->
<!-- ```{r} -->
<!-- library(qrbp) -->
<!-- set.seed(123) -->
<!-- n <- 200 -->
<!-- bkpts <- qrbp(n,dimension = 2,known.sites=ks,include.known.sites=TRUE, -->
<!--               study.area = sa,inclusion.probs = NULL,sigma=1,plot.prbs=TRUE) -->
<!-- points(ks$x1,ks$x2,pch=16,col='white') -->
<!-- ``` -->

Import some species data and covariates for modelling
```{r,message=FALSE}
library(sdm)
library(rgdal)
library(raster)

file <- system.file("external/species.shp", package="sdm") # 
species <- shapefile(file)
path <- system.file("external", package="sdm") # path to the folder contains the data
lst <- list.files(path=path,pattern='asc$',full.names = T) 
preds <- stack(lst)
projection(preds) <- "+proj=merc +lon_0=0 +k=1 +x_0=0 +y_0=0 +a=6378137 +b=6378137 +units=m +no_defs"
```

plot the presence only data (occurrences==1), in the dataset we have the luxury of absences which means that if you were going to model this species correctly, you could do it using absences and have no need generate background points.
```{r}
plot(preds[[1]])
points(species[species$Occurrence == 1,],col='red',pch=16,cex=.5)
```

For a laugh, let's generate some quasirandom background points and plot them against the presence points
```{r}
library(qrbp)
POdata <- species[species$Occurrence == 1,]
bkpts <- generate_background_points(number_of_background_points = 10000,
                                    known_sites = POdata@coords,
                                    study_area = preds[[1]],
                                    model_covariates = preds,
                                    method = 'quasirandom')

```

Now let's plot our background points
```{r}
plot(preds[[1]])
points(bkpts[bkpts$presence == 0,c("x","y")],col='blue',pch=16,cex=.5)
points(bkpts[bkpts$presence == 1,c("x","y")],col='red',pch=16,cex=1)
```

Now let's try and generate a ppm using a poisson gam
```{r, warning=FALSE}
library(mgcv)
fm1 <- gam(presence ~ s(elevation) +
              s(precipitation) +
              s(temperature) +
              s(vegetation) + 
              offset(log(weights)),
              data = bkpts,
              family = poisson())

p <- predict(object=preds,
             model=fm1,
             type = 'response',
             const=data.frame(weights = 1))

p_cell <- p*res(preds)[1]*res(preds)[2]

plot(p_cell)
```

Let's compare to a PA sdm - hopefully we are in the right ball park
```{r,message=FALSE,error=FALSE,warning=FALSE}
d <- sdmData(formula= ~., train=species, predictors=preds)
m1 <- sdm(Occurrence~.,data=d,methods=c('gam'))
p1 <- predict(m1,newdata=preds)
plot(p1)
```
### References 
Grafström, Anton, and Yves Tillé. "Doubly balanced spatial sampling with spreading and restitution of auxiliary totals." Environmetrics 24.2 (2013): 120-131.
